---
format: 
  html:
    self-contained: true
    css: 
      - ../assets/webex.css
    include-after-body: 
      - ../assets/webex.js
---

```{r}
#| include: false
library(webexercises)
```

* Once again, for each exercise make the targetted plot shown. 

### Factorial experiment of bermuda grass with nitrogen (n), phosphorus (p), and potassium (k) fertilizers 

```{webr-r}
#| autorun: true
data(welch.bermudagrass, package = "agridat")
str(welch.bermudagrass)
```

::: {.panel-tabset}

## Exercise 2A



```{r echo = FALSE, class = "target"}
ggplot(welch.bermudagrass, aes(yield, fill = factor(n))) + 
  geom_density(alpha = 0.2) 
```

```{webr-r}
ggplot(welch.bermudagrass, aes(___)) + 
  geom____(alpha = 0.2)
```

## Exercise 2B

Now try changing the y-axis so it shows `count` instead of `density`.

```{r echo = FALSE, class = "target"}
ggplot(welch.bermudagrass, aes(yield, fill = factor(n))) + 
  geom_density(alpha = 0.2, aes(y = after_stat(count))) 
```


```{webr-r}
ggplot(welch.bermudagrass, aes(___)) + 
  geom____(alpha = 0.2, 
           aes(___)) 
```

## Exercise 2C

Now make the position adjustment so the density is stacked.

```{r echo = FALSE, class = "target"}
ggplot(welch.bermudagrass, aes(yield, fill = factor(n))) + 
  geom_density(alpha = 0.2, position = "stack") 
```


```{webr-r}
ggplot(welch.bermudagrass, aes(___)) + 
  geom____(alpha = 0.2, ___) 
```


## Exercise 2D

Adjust the position to show the density as a proportion of the total across the yield like the graph below.

```{r echo = FALSE, class = "target"}
ggplot(welch.bermudagrass, aes(yield, fill = factor(n))) + 
  geom_density(alpha = 0.2, position = "fill") 
```


```{webr-r}
ggplot(welch.bermudagrass, aes(___)) + 
  geom____(alpha = 0.2, ___) 
```

:::


### Randomized Trial of Six Therapies for Scurvy

```{webr-r}
#| autorun: true
data(scurvy, package = "medicaldata")
str(scurvy)
```

::: {.panel-tabset}

## Exercise 2E

```{r echo = FALSE, class = "target"}
ggplot(scurvy, aes(gum_rot_d6, fill = skin_sores_d6)) + 
  geom_bar()
```


```{webr-r}
ggplot(scurvy, aes(___, fill = ___)) + 
  geom____()
```

## Exercise 2F

```{r echo = FALSE, class = "target"}
ggplot(scurvy, aes(gum_rot_d6, fill = skin_sores_d6)) + 
  geom_bar(position = position_dodge2(preserve = "single"))
```


```{webr-r}
ggplot(scurvy, aes(___, fill = ___)) + 
  geom____(position = position_dodge2(preserve = ___))
```

## Exercise 2G

```{r echo = FALSE, class = "target"}
ggplot(scurvy, aes(gum_rot_d6, fill = skin_sores_d6)) + 
  geom_bar(position = "fill")
```


```{webr-r}
ggplot(scurvy, aes(___, fill = ___)) + 
  geom____(position = ___)
```

## Exercise 2H

```{r echo = FALSE, class = "target"}
ggplot(scurvy, aes(gum_rot_d6, fill = skin_sores_d6)) + 
  geom_bar(position = "fill") +
  coord_polar("y")
```


```{webr-r}
ggplot(scurvy, aes(___, fill = ___)) + 
  geom____(position = ___) +
  coord____
```


:::